Assignment 5

### 2015-02-25 rmtw/a5/latex8.tex
Changes, they have been made
asd

Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}. However, why then do most large software companies chose not to adopt MDSD?

@@

@@

\item Selection of primary studies (6.2)
\item Study quality assessment (6.3)
\item Data extraction and monitoring (6.4)
\item Data synthesis
\end{itemize}

>>>>

Academia appears to be united in the opinion that MDSD is an improvement compared with traditional software development \cite{staron2006adopting} \cite{volter2013model}. However, why do many large software companies chose not to adopt MDSD?

@@

Protocol
1. Search process (table)
2. Incl
include search terms here and databases

3. Excl

Informal literature surveys (no defined research questions, no search process, no
defined data extraction or data analysis process). 
• Papers not subject to peer-review. 
non english

Make a table somwhere stating that william picks some and john checks the same vice versa.

4. Tabulate the findings (overview)

5. check the data colleciton part

@@

\item Selection of primary studies (6.2)
\item Study quality assessment (6.3) x
\item Data extraction and monitoring (6.4) x
\item Data synthesis x
\end{itemize}
